Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-06 article.tex
Do evolution with human, viral and bacterial TMHs
Simplified hypotheses

\begin{itemize}
  \item $\mathcal{H}_{1,1}$: MHC-I has the same percentage of epitopes overlapping
    with TMHs in Homo sapiens as in COVID-19
  \item $\mathcal{H}_{1,2}$: MHC-I has the same percentage of epitopes overlapping
    with TMHs in Homo sapiens as in Mycobacterium
  \item $\mathcal{H}_{2,1}$: MHC-II has the same percentage of epitopes overlapping
    with TMHs as expected by chance in Homo sapiens
  \item $\mathcal{H}_{2,2}$: MHC-II has the same percentage of epitopes overlapping
    with TMHs as expected by chance in COVID-19
  \item $\mathcal{H}_{2,3}$: MHC-II has the same percentage of epitopes overlapping
    with TMHs as expected by chance in Mycobacterium
  \item $\mathcal{H}_{3,1}$: MHC-II haplotypes will display epitopes
    of a certain hydrophobicity, that is as likely to stem from
    a TMH or a non-TMH 13-mer as expected by chance
  \item $\mathcal{H}_{3,2}$: MHC-II haplotypes that have hydrophobic
    binding pockets, will display more epitopes derived from (hydrophobic)
    TMHs
  \item $\mathcal{H}_{3,3}$: MHC-II haplotypes that have binding pockets
    that are only partly hydrophobic, will display more epitopes derived 
    from the flanking regions of TMHs
  \item $\mathcal{H}_{4,1}$: The TMHs of COVID-19
    have the same mutation rate 
    as the cytosolic and extracellular parts of their transmembrane proteins
  \item $\mathcal{H}_{4,2}$: The TMHs of Mycobacterium
    have the same mutation rate 
    as the cytosolic and extracellular parts of their transmembrane proteins
\end{itemize}

@@

To detect evolution, we determine the probability 
that all of the observed TMH mutations have arisen by chance,
with regards to being detected/presented by the immune system,
per MHC class and haplotype.

>>>>

\begin{itemize}
  \item $\mathcal{H}_{1,VB}$: MHC-I has the same percentage of epitopes overlapping
    with viral/bacterial TMHs as with human TMHs
  \item $\mathcal{H}_{2,HVB}$: MHC-II has the same percentage of epitopes overlapping
    with human/viral/bacterial TMHs as expected by chance
  \item $\mathcal{H}_{3,HVB}$: The mutations observed in 
    human/viral/bacterial TMHs are caused by chance.
    Alternatively, these are caused by natural selection
    induced by binding to HLAs
\end{itemize}

@@

To detect evolution, we determine the probability 
that all of the observed TMH mutations have arisen by chance,
with regards to being detected/presented by the immune system,
per MHC class and haplotype. We do this for human, viral and
bacterial TMHs.
